---
title: "Introduction to the Coronavirus Dataset"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to the Coronavirus Dataset}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

### The Coronavirus Dataset

The {covidvirus} package comes with one function `get_cases()` that retrieves a daily snapshot of confirmed, death, and recovered cases from the Johns Hopkins University Center for Systems Science and Engineering (JHU CCSE) Coronavirus [repository](https://github.com/CSSEGISandData/COVID-19).


```{r setup}
library(covidvirus)
corona_virus <- covidvirus::get_cases()
```


The retrieved data consists of the following columns:

- `province_state`: the province or state within the country (if applicable)
- `country-region`: the country or region name
- `lat`: the latitude
- `long`: the longitude
- `date`: the date of the summary
- `type`: the classification of the case (e.g., infected, death, recovered)
- `cases`: the total number of cases observed daily

The returned dataset is a tibble and we can easily leverage any tidyverse compatible function.

Let's take a look at the first few rows and the structure:

```{r}
head(corona_virus)
```

```{r}
dplyr::glimpse(corona_virus)
```


### Brief Analysis

Let's dive a bit into the data. We'll use the following libraries: `dplyr`.

```{r, echo=FALSE}
library(dplyr)
```


#### Total cases by Type

```{r}

corona_virus %>%
  group_by(type) %>%
  summarize(
    total_cases = sum(cases)
  ) %>%
  ungroup()
```

#### Total cases by each country/region

```{r}
corona_virus %>%
  group_by(country_region) %>%
  summarize(
    total_cases = sum(cases)
  ) %>%
  ungroup() %>%
  arrange(desc(total_cases))
```

